---
title: "EpibibR: Vignette"
author: "Thierry Warin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Practical usage

## Quick start

First, install EpiBibR:

```{r, eval=FALSE}
devtools::install_github("warint/EpiBibR")
```

Next, call EpiBibR to make sure everything is installed correctly.

```{r}
library(EpiBibR)
```


## How-To 

These functions are still available, but we have developed a new function that synthesizes them. 'epibib_data()' Practical Guide is accessible [here](https://warint.github.io/EpiBibR/articles/vignette.html)


EpiBibR allows you to search bibligraphic references using several arguments : Author, author's country of origin, author + year, keywords in the title, keywords in the abstract, year and source name.

### Retrieve bibliographic data

To get the entire bibliographic dataframe contaning more than 80 000 references, use the `EpiBib_reference` function.

```{r,eval=FALSE}
EpiBib_data <- EpiBib_references()
```

### Search by author

It can be truly helpful to search references by the name of the author. For example, we will search all the articles writtin by Philippe Colson.

```{r,eval=FALSE}
colson_articles <- EpiBib_author("Colson")
```

### Search by author's country of origin.

```{r,eval=FALSE}
canada_articles <- EpiBib_country("canada")
```

### Search by author and year

```{r,eval=FALSE}
yang2019 <- EpiBib_AU_YE(author = "yang", year = 2019)
```

### Search by keywords in title

```{r,eval=FALSE}
covid_articles <- EpiBib_title("covid")
```

### Search by keywords in the abstract

```{r,eval=FALSE}
coronavirus_articles <- EpiBib_abstract("coronavirus")
```

### Search by year

```{r,eval=FALSE}
A2020_articles <- EpiBib_year(2020)
```

### Search by source

```{r,eval=FALSE}
bio_articles <- EpiBib_source("bio")
```



